Reference

### 2019-08-27 content/reference.Rmd
Update for first day!

@@

# Citations and bibliography

[^bibtex] You can [download a BibTeX file](/bib/references.bib) of all the non-web-based readings in the course.

[^bibtex]: {-} You can open the file in [BibDesk on macOS](http://bibdesk.sourceforge.net/), [JabRef on Windows](http://www.jabref.org/), or [Zotero](https://www.zotero.org/) or [Mendeley](https://www.mendeley.com/) online.

>>>>

Look here over the course of the semester for resources, links, and tips on how to succeed in the course, how to write well, and other things of interest related to econometrics, data analysis, managing your worfklow, and using R.

@@
